Distributed Topology Discovery in Self-Assembled Nano Networks

### 2014-02-18 PAPER/paper.tex
Removed some typos

\documentclass[final,journal]{IEEEtran}
%\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{cite}
\usepackage{balance}
\usepackage{float}
\usepackage{threeparttable}

@@

\author{Vincenzo~Catania, Andrea Mineo, Salvatore Monteleone~and~Davide~Patti% 
\thanks{The authors are with the Dipartimento di Ingegneria
Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
(email: \{vincenzo.catania,amineo,salvatore.monteleone,davide.patti\}@dieei.unict.it).}}

\maketitle

\begin{abstract}
In this paper we present \disr{}, a distributed approach to topology
discovery and defect mapping in a self-assembled nano
networks-on-chip. The main aim is achieving the already-proven
properties of segment-based deadlock freedom without neither requiring
a topology graph as input, nor needing a centralized algorithm to
configure network paths.  After introducing the conceptual elements
and the execution model of \disr{}, we show how the opensource Nanoxim
platform has been used to evaluate the proposed approach in the
process of discovering irregular network topology while establishing
network segments. Comparison against a tree-based approach show how
\disr{} still preserves some important properties (coverage, defect
tolerance, scalability) while avoiding resource hungry solutions such
as virtual channels and hardware redundancy. Finally, we propose a
gate-level hardware implementation of the required control logic and
storage for \disr{}, demonstrating a relatively acceptable impact
ranging from 10 to about 20\% of the budget of transistors available
for each node.
\end{abstract}

%------------------------------------------------------------------------------
%\IEEEkeywords{...}

\begin{IEEEkeywords}
Nanotechnology, DNA, Self-assembly, Routing, Deadlock
\end{IEEEkeywords}
%------------------------------------------------------------------------------

>>>>

%\documentclass[final,journal]{IEEEtran}
%\IEEEoverridecommandlockouts

% Elsevier specific styles
%------------------------------------------------------------------------------
\documentclass[review]{elsarticle}
%\documentclass[3p]{elsarticle}
\usepackage{lineno,hyperref}

\modulolinenumbers[5]

\journal{Journal of \LaTeX\ Templates}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
%------------------------------------------------------------------------------
%\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{balance}
\usepackage{float}
\usepackage{threeparttable}

@@

\begin{abstract}
In this paper we present \disr{}, a distributed approach to topology
discovery and defect mapping in a self-assembled nano
network-on-chip. The main aim is achieving the already-proven
properties of segment-based deadlock freedom without neither requiring
a topology graph as input, nor needing a centralized algorithm to
configure network paths.  After introducing the conceptual elements
and the execution model of \disr{}, we show how the open-source Nanoxim
platform has been used to evaluate the proposed approach in the
process of discovering irregular network topology while establishing
network segments. Comparison against a tree-based approach shows how
\disr{} still preserves some important properties (coverage, defect
tolerance, scalability) while avoiding resource hungry solutions such
as virtual channels and hardware redundancy. Finally, we propose a
gate-level hardware implementation of the required control logic and
storage for \disr{}, demonstrating a relatively acceptable impact
ranging from 10 to about 20\% of the budget of transistors available
for each node.
\end{abstract}

%------------------------------------------------------------------------------
\begin{keyword}
Nanotechnology \sep DNA \sep Self-assembly \sep Routing \sep Deadlock
\end{keyword}
\end{frontmatter}
%------------------------------------------------------------------------------
